---
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(ggplot2)
library(corrplot)
library(caret)
library(corrplot)
```


```{r}
diabetes <- read.csv("C:/Users/chvka/Downloads/archive (4)/diabetes.csv")
head(diabetes)
```

dimentions

```{r}
dim(diabetes)
```
```{r}
names(diabetes)
```


```{r}
table(diabetes$Outcome)
```


rename

```{r}
library(tidyverse)
d2<-diabetes %>%
  rename("Glucose_mg/dl" = Glucose,
         "BloodPressure_mmHg"= BloodPressure,
         "Insulin_mL"=Insulin,
         "BMI_W/H"=BMI,
         "DiabetesPedigreeFunction_%"=DiabetesPedigreeFunction)
  
```


arrange by age.



```{r}
d3 <- d2 %>%
  arrange(Age)
head(d3)
```

Diabetic patients table

```{r}
yes<-diabetes %>% 
  filter(Outcome==0)
head(yes)
```


non diabetic 

```{r}
no<-diabetes %>% 
  filter(Outcome==1)
head(no)
```


mean, standard deviation and count 

```{r}
table1<- yes %>%
  group_by(Outcome)%>%
  summarize(count=length(Outcome),
            mean_Pregnancies=mean(Pregnancies),
            SD_Pregnancies=sd(Pregnancies),
            mean_Glucose= mean(Glucose),
            SD_Glucose = sd(Glucose),
            mean_BloodPressure= mean(BloodPressure),
            SD_BloodPressure= sd(BloodPressure),
            mean_SkinThickness = mean(SkinThickness),
            SD_SkinThickness = sd(SkinThickness),
            mean_Insulin=mean(Insulin),
            SD_Insulin= sd(Insulin),
            mean_BMI= mean(BMI),
            SD_BMI= sd(BMI),
            mean_DiabetesPedigreeFunction= mean(DiabetesPedigreeFunction),
            SD_DiabetesPedigreeFunction = sd(DiabetesPedigreeFunction),
            )
head(table1)
```

```{r}
table2<- no %>%
  group_by(Outcome)%>%
  summarize(count=length(Outcome),
            mean_Pregnancies=mean(Pregnancies),
            SD_Pregnancies=sd(Pregnancies),
            mean_Glucose= mean(Glucose),
            SD_Glucose = sd(Glucose),
            mean_BloodPressure= mean(BloodPressure),
            SD_BloodPressure= sd(BloodPressure),
            mean_SkinThickness = mean(SkinThickness),
            SD_SkinThickness = sd(SkinThickness),
            mean_Insulin=mean(Insulin),
            SD_Insulin= sd(Insulin),
            mean_BMI= mean(BMI),
            SD_BMI= sd(BMI),
            mean_DiabetesPedigreeFunction= mean(DiabetesPedigreeFunction),
            SD_DiabetesPedigreeFunction = sd(DiabetesPedigreeFunction),
            )

head(table2)
```


combining both tables 


```{r}
t3 <- full_join(table1,table2)
tibble(t3)
head(t3)
```


pLOTS 

```{r}
ggplot(diabetes,aes(x=Outcome,y=Insulin,color=Outcome))+
geom_point()
```



```{r}

plot2 <- ggplot(data=diabetes,
aes(x=Outcome,y=Pregnancies,col=Pregnancies))+geom_point()
plot2
```



```{r}
p <- ggplot(data=diabetes,aes(x=Pregnancies,y=Glucose,color=factor(Outcome)))+
geom_point()
plot1 <- p+
facet_grid(Outcome~.,)+
theme(plot.background=element_rect(colour="black"))
plot1
```


Here is a dot plot for the chance of being diabetic when there are more number of pregnancies.

The other plot gives us information about glucose level of the women on y and number of pregnancies on x.

The glucose level is high for women when they are not diabetic.

```{r}
plot_age <- ggplot(data=diabetes,
             aes(x=Age,y=Glucose,color=factor(Outcome)))+geom_point()
plot_age+facet_grid(Outcome~.,)
```


corelation plot
```{r}
numeric.var <- sapply(diabetes, is.numeric)
corr.matrix <- cor(diabetes[,numeric.var])
corrplot(corr.matrix, main="\n\nCorrelation Plot ", order = "hclust", tl.col = "black", tl.srt=45, tl.cex=0.8, cl.cex=0.8)
box(which = "outer", lty = "solid")
```


logistic regression

```{r}
train <- diabetes[1:540,]
test <- diabetes[541:768,]
```


```{r, include=FALSE}
lm <- glm(as.factor(Outcome)~.,data=train,family=binomial)
summary(lm)

```

```{r}
lm2 <- step(lm)
summary(lm2)
AIC(lm,lm2)
```


```{r}
fitted.results <- predict(lm2,newdata=test,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)
(conf_matrix_logi<-table(fitted.results, test$Outcome))
```




